Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-11 main.tex
Change results pictures - main result picture made much more legible (as pointed out by reviewer) - timing picture made smaller and correctly centered - layouts picture made smaller, correctly centered, and added covariance to the legend - made tikz pictures smaller (not by scaling but by moving the pics objects so that it fits in less space Still not 12 pages but very close

At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$. Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$. This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and Combination Step};
    % Navigator
    \fill (3.25,4.5) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [blue!80!black!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [blue!80!black!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (2.125,3.375) rectangle (4.375,2.625);
    \node at (3.25,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,-0.75) {2. Aggregation Step};
    % Navigator
    \fill [green!80!black!60] (1.375,-3) rectangle (5.125,-1.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-5.875) {Sensor $1$};
    \fill  (5.25,-5.25) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (5.25,-5.875) {Sensor $n$};
    \fill  (1.25,-5.25) [blue!80!black!40] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-5.25) circle (0.05);
    \fill [black] (3.75,-5.25) circle (0.05);
    \fill [black] (3.25,-5.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-4.75) (3.75,-3.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-4.75) (2.75,-3.25)};
    \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
    \node at (2,-4) {$l_1^{(t)}$};
    \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
    \node at (4.625,-4) {$l_n^{(t)}$};

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,0);
    \draw [gray] (0,-0.25) rectangle (6.5,-6.25);
\end{tikzpicture}
\caption{Required linear combination aggregation steps at instance $t$.}
\label{fig:agg_steps}
\end{figure}
In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.

@@

Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have also been summarised graphically in figure \ref{fig:alg_steps}. Here, for brevity, $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ denote elementwise operations with the same parameters.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Prediction
    \draw [gray] (0,2) rectangle (6.5,8);
    \node at (3.25,7.5) {\small 1. Prediction};

    % Navigator
    \fill  [green!80!black!60] (2,7) rectangle (4.5,5.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
    \node at (3.25,5.875) {$\hat{\vec{x}}_{k|k-1}$, $\mat{P}_{k|k-1}$};

    % Sensors
    \fill  (1.25,3) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (1.25,2.375) {Sensor $1$};
    \fill  (5.25,3) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (5.25,2.375) {Sensor $n$};

    \fill [black] (2.75,3) circle (0.05);
    \fill [black] (3.25,3) circle (0.05);
    \fill [black] (3.75,3) circle (0.05);

    % Arrows
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,5.25) (1.5,3.5)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,5.25) (5,3.5)};

    \fill [lightgray]  (0.25,5) rectangle (6.25,4);
    \node at (3.25,4.5) {$\left\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\omega)) \,|\, \omega \!\in\! \{\hat{x}^3_{k|k-1}, \hat{y}^3_{k|k-1}, \dots\}\right\rangle$};

    % Measurement
    \draw [gray] (0,-4.25) rectangle (6.5,1.75);
    \node at (3.25,1.25) {\small 2. Measurement};

    % Navigator
    \fill  (3.25,0.25) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,0.4225) {plane};

    % Sensors
    \fill  [blue!80!black!40] (6.25,-3.625)  rectangle (4.25,-2.625);
    \node at (1.25,-3.875) {Sensor $1$};
    \fill  [blue!80!black!40] (2.25,-3.625)  rectangle (0.25,-2.625);
    \node at (5.25,-3.875) {Sensor $n$};

    \node at (1.25,-3.125) {$z'_{k,1}$, $r'_{k,1}$};
    \node at (5.25,-3.125) {$z'_{k,n}$, $r'_{k,n}$};

    \fill [black] (2.75,-3.125) circle (0.05);
    \fill [black] (3.25,-3.125) circle (0.05);
    \fill [black] (3.75,-3.125) circle (0.05);

    % Arrows
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.25,-2.5) (3,-0.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5.25,-2.5) (3.5,-0.25)};

    \fill [lightgray]  (0.375,-0.875) rectangle (3.125,-1.875);
    \node[align=center] at (1.75,-1.375) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\vec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
    \fill [lightgray]  (3.375,-0.875) rectangle (6.125,-1.875);
    \node[align=center] at (4.75,-1.375) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\vec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};

    % Update
    \draw [gray] (0,-8.5) rectangle (6.5,-4.5);
    \node at (3.25,-5) {\small 3. Update};

    % Navigator
    \fill  [green!80!black!60] (1.5,-5.5) rectangle (5,-7.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-5.8275) {plane};
    \node at (3.25,-6.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
    \node at (3.25,-7.125) {$\hat{\vec{x}}_{k|k}$, $\mat{P}_{k|k}$};
\end{tikzpicture}
\caption{Procedure at timestep $k$ for the proposed privacy-preserving EIF.}
\label{fig:alg_steps}
\end{figure}

@@

We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r'_{k,i}$ on the original measurements $z_{k,i}$. These layouts of varying sensor distances to the navigator track are shown in figure \ref{fig:sim_layouts}.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/layouts.pdf}
    \caption{Diffrent simulation layouts with varying average distances between navigator and sensors.}
    \label{fig:sim_layouts}
\end{figure}
To demonstrate the accuracy of the method, we have compared the root mean square error (RMSE) of the privacy-preserving filter to the standard EIF using unmodified measurements, that is algebraically equivalent to the EKF, typically used in industry for linearising non-linear state estimation. Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times. Unmodified measurement variances were taken as $r_{k,i}=5$ for all $k>0$ and a large fractional precision factor, $\phi=2^{32}$, was chosen. The results can be seen in figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/layout_errors.pdf}
    \caption{MSE of the privacy-preserving EIF and standard EIF for different layout simulations.}
    \label{fig:sim_layout_errors}
\end{figure}
From these results, we can see the similarity in filter performance between the privacy-preserving method and that of the traditional EIF. We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance. We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.

>>>>

At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$. Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$. This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and Combination Step};
    % Navigator
    \fill (3.25,4.75) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
    % Sensors
    \node at (1.5,1.375) {Sensor $1$};
    \fill [blue!80!black!40] (0.25,1.625) rectangle (2.875,2.625);
    \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,1.375) {Sensor $n$};
    \fill [blue!80!black!40] (3.625,1.625) rectangle (6.25,2.625);
    \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,2.125) circle (0.05);
    \fill [black] (3,2.125) circle (0.05);
    \fill [black] (3.25,2.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4.25) (5,2.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4.25) (1.5,2.875)};
    \fill [lightgray] (2.125,3.875) rectangle (4.375,3.125);
    \node at (3.25,3.5) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,0.25) {2. Aggregation Step};
    % Navigator
    \fill [green!80!black!60] (1.375,-2) rectangle (5.125,-0.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-0.4775) {plane};
    \node at (3.25,-1.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-3.875) {Sensor $1$};
    \fill  (5.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (5.25,-3.875) {Sensor $n$};
    \fill  (1.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-3.25) circle (0.05);
    \fill [black] (3.75,-3.25) circle (0.05);
    \fill [black] (3.25,-3.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-2.75) (4.5,-2.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-2.75) (2,-2.25)};
    \fill [lightgray] (1.625,-2.5) rectangle (2.25,-3);
    \node at (2,-2.75) {$l_1^{(t)}$};
    \fill [lightgray] (4.25,-2.5) rectangle (4.875,-3);
    \node at (4.625,-2.75) {$l_n^{(t)}$};

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,1);
    \draw [gray] (0,0.75) rectangle (6.5,-4.25);
\end{tikzpicture}
\caption{Required linear combination aggregation steps at instance $t$.}
\label{fig:agg_steps}
\end{figure}
In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.

@@

Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have also been summarised graphically in figure \ref{fig:alg_steps}. Here, for brevity, $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ denote elementwise operations with the same parameters.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Prediction
    \draw [gray] (0,3) rectangle (6.5,8);
    \node at (3.25,7.5) {\small 1. Prediction};

    % Navigator
    \fill  [green!80!black!60] (2,7) rectangle (4.5,5.75);
    \pic[xscale=0.22,yscale=0.3] at (3.25,6.7975) {plane};
    \node at (3.25,6.0625) {$\hat{\vec{x}}_{k|k-1}$, $\mat{P}_{k|k-1}$};

    % Sensors
    \fill  (1.25,4) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (1.25,3.375) {Sensor $1$};
    \fill  (5.25,4) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (5.25,3.375) {Sensor $n$};

    \fill [black] (2.75,4) circle (0.05);
    \fill [black] (3.25,4) circle (0.05);
    \fill [black] (3.75,4) circle (0.05);

    % Arrows
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,5.5) (1.75,4.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,5.5) (4.75,4.25)};

    \fill [lightgray]  (0.25,5.375) rectangle (6.25,4.625);
    \node at (3.25,5) {$\left\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\omega)) \,|\, \omega \!\in\! \{\hat{x}^3_{k|k-1}, \hat{y}^3_{k|k-1}, \dots\}\right\rangle$};

    % Measurement
    \draw [gray] (0,-2.25) rectangle (6.5,2.75);
    \node at (3.25,2.25) {\small 2. Measurement};

    % Navigator
    \fill  (3.25,1.5) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,1.6725) {plane};

    % Sensors
    \fill  [blue!80!black!40] (6.25,-1.625)  rectangle (4.25,-0.625);
    \node at (1.25,-1.875) {Sensor $1$};
    \fill  [blue!80!black!40] (2.25,-1.625)  rectangle (0.25,-0.625);
    \node at (5.25,-1.875) {Sensor $n$};

    \node at (1.25,-1.125) {$z'_{k,1}$, $r'_{k,1}$};
    \node at (5.25,-1.125) {$z'_{k,n}$, $r'_{k,n}$};

    \fill [black] (2.75,-1.125) circle (0.05);
    \fill [black] (3.25,-1.125) circle (0.05);
    \fill [black] (3.75,-1.125) circle (0.05);

    % Arrows
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.25,-0.5) (3,1)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5.25,-0.5) (3.5,1)};

    \fill [lightgray]  (0.375,0.75) rectangle (3.125,-0.25);
    \node[align=center] at (1.75,0.25) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\vec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
    \fill [lightgray]  (3.375,0.75) rectangle (6.125,-0.25);
    \node[align=center] at (4.75,0.25) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\vec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};

    % Update
    \draw [gray] (0,-5.75) rectangle (6.5,-2.5);
    \node at (3.25,-3) {\small 3. Update};

    % Navigator
    \fill  [green!80!black!60] (1.5,-3.5) rectangle (5,-5.5);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-3.8275) {plane};
    \node at (3.25,-4.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
    \node at (3.25,-5.125) {$\hat{\vec{x}}_{k|k}$, $\mat{P}_{k|k}$};
\end{tikzpicture}
\caption{Procedure at timestep $k$ for the proposed privacy-preserving EIF.}
\label{fig:alg_steps}
\end{figure}

@@

We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r'_{k,i}$ on the original measurements $z_{k,i}$. These layouts of varying sensor distances to the navigator track are shown in figure \ref{fig:sim_layouts}.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/layouts.pdf}
    \caption{Different simulation layouts with varying distances between navigator and sensors.}
    \label{fig:sim_layouts}
\end{figure}
To demonstrate the accuracy of the method, we have compared the root mean square error (RMSE) of the privacy-preserving filter to the standard EIF using unmodified measurements, that is algebraically equivalent to the EKF, typically used in industry for linearising non-linear state estimation. Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times. Unmodified measurement variances were taken as $r_{k,i}=5$ for all $k>0$ and a large fractional precision factor, $\phi=2^{32}$, was chosen. The results can be seen in figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/layout_errors.pdf}
    \caption{Average RMSE of our privacy-preserving filter and the standard EIF for different layouts.}
    \label{fig:sim_layout_errors}
\end{figure}
From these results, we can see the similarity in filter performance between the privacy-preserving method and that of the traditional EIF. We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance. We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
